---
title: "Meta-Analysis"
output: html_document
date: "2023-07-14"
---
```{r message=FALSE}
library("plyr")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("ggpubr")
library("lme4") # for models
library("sjPlot") # for models
library("sjmisc") # for models
library("MuMIn") # getting R squared from mixed models
library("effects")
library("ggeffects")
library("lmerTest")
library("metafor")
library("meta")
library("esc")
library("purrr")
```

Notes
- ALGAE: is anytime a study wasn't specific about what type of algae its talking about
- Macroalgae: not CCA, not turf


https://wviechtb.github.io/metafor/reference/robust.html
https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/multilevel-ma.html
https://www.metafor-project.org/doku.php/tips:forest_plot_with_aggregated_values
http://www.metafor-project.org/doku.php/analyses:konstantopoulos2011 
https://www.metafor-project.org/doku.php/tips:rma.uni_vs_rma.mv 



# (1) Data Wrangling
Full data
```{r}
data <- read.csv("../data/final_data_extracted.csv")
View(data)

# Create Metadata 
test <- data %>% select(1:28) # filter out columns

# Group by each study so we only have one row per study
metadata <- test %>% 
        group_by(unique_ID, last_name, year_published, region, 
                 location, study_duration_mm, tile_conditioning_mm) %>% 
        summarize(mean_herb_biomass = mean(herbivore_biomass_gm2))

# Create a new variable of a study number for each unique id
data[,"study_num"] <- NA
data$study_num <- as.numeric( sub("\\D*(\\d+).*", "\\1", data$unique_ID) )
```
study_num column --> takes only the unique identifier numbers from the unique_ID column and stores in new column




# (2) Calculate Effect Sizes

```{r}
##### Coral #####
#################
# Calculate effect size
coral_effect_size.1 <- escalc(measure="SMD", m1i=coral_uncaged_mean, m2i=coral_caged_mean, 
                            sd1i=coral_uncaged_SD, sd2i=coral_caged_SD, 
                            n1i=coral_uncaged_n, n2i=coral_caged_n, 
                            data=data, slab=paste(last_name, year_started, location, site, sep=", "))
#Warning: Some 'yi' and/or 'vi' values equal to +-Inf. Recoded to NAs.

# Select columns
coral_effect_size.2 <- coral_effect_size.1 %>% 
        select(c('unique_ID', 'paper', 'unique_ID_site', 'study_num', 'cluster_ID', 'coral_recruit_location', 'yi','vi', "herbivore_biomass_gm2", "study_duration_mm", "MPA_paper"))

# Remove NA's
coral_effect_size <- coral_effect_size.2 %>% 
        subset(!is.na(yi)) %>%
  mutate(esid=row_number()) 







##### ALGAE #####
#################
ALGAE_effect_size.1 <- escalc(measure="SMD", m1i=ALGAE_uncaged_mean, m2i=ALGAE_caged_mean, 
                            sd1i=ALGAE_uncaged_SD, sd2i=ALGAE_caged_SD, 
                            n1i=ALGAE_uncaged_n, n2i=ALGAE_caged_n, 
                            data=data, slab=paste(last_name, year_started, location, site, sep=", "))

ALGAE_effect_size.2 <- ALGAE_effect_size.1 %>% select(c('unique_ID', 'paper', 'unique_ID_site', 'study_num', 'cluster_ID', 'yi','vi',"herbivore_biomass_gm2","study_duration_mm"))


ALGAE_effect_size <- ALGAE_effect_size.2 %>% 
        subset(!is.na(yi))%>%
  mutate(esid=row_number())
      



##### Turf #####
#################
turf_effect_size.1 <- escalc(measure="SMD", m1i=turf_uncaged_mean, m2i=turf_caged_mean, 
                           sd1i=turf_uncaged_SD, sd2i=turf_caged_SD, 
                           n1i=turf_uncaged_n, n2i=turf_caged_n, 
                           data=data, slab=paste(last_name, year_started, location, site, sep=", "))

turf_effect_size.2 <- turf_effect_size.1 %>% select(c('unique_ID', 'paper', 'unique_ID_site','study_num', 'cluster_ID', 'turf_cluster_ID', 'yi','vi',"herbivore_biomass_gm2","study_duration_mm"))

turf_effect_size <- turf_effect_size.2 %>% 
        subset(!is.na(yi))%>%
  mutate(esid=row_number()) 





##### Macroalgae #####
######################
macroalgae_effect_size.1 <- escalc(measure="SMD", m1i=macroalgae_uncaged_mean, m2i=macroalgae_caged_mean,
                                 sd1i=macroalgae_uncaged_SD, sd2i=macroalgae_caged_SD, 
                                 n1i=macroalgae_uncaged_n, n2i=macroalgae_caged_n, 
                                 data=data, slab=paste(last_name, year_started, location, site, sep=", "))

macroalgae_effect_size.2 <- macroalgae_effect_size.1 %>% select(c('unique_ID', 'paper', 'unique_ID_site','study_num', 'cluster_ID', 'macro_cluster_ID', 'yi','vi',"herbivore_biomass_gm2","study_duration_mm"))

macroalgae_effect_size <- macroalgae_effect_size.2 %>% 
        subset(!is.na(yi)) %>%
  mutate(esid=row_number())







##### CCA #####
###############
CCA_effect_size.1 <- escalc(measure="SMD", m1i=CCA_uncaged_mean, m2i=CCA_caged_mean, 
                          sd1i=CCA_uncaged_SD, sd2i=CCA_caged_SD, 
                          n1i=CCA_uncaged_n, n2i=CCA_caged_n, 
                          data=data, slab=paste(last_name, year_started, location, site, sep=", "))

CCA_effect_size.2 <- CCA_effect_size.1 %>% select(c('unique_ID', 'paper', 'unique_ID_site', 'study_num', 'cluster_ID', 'yi','vi',"herbivore_biomass_gm2","study_duration_mm"))

CCA_effect_size <- CCA_effect_size.2 %>% 
        subset(!is.na(yi)) %>%
  mutate(esid=row_number())






##### Invertebrates #####
#########################
invertebrates_effect_size.1 <- escalc(measure="SMD", m1i=invertebrates_uncaged_mean, m2i=invertebrates_caged_mean, 
                                    sd1i=invertebrates_uncaged_SD, sd2i=invertebrates_caged_SD, 
                                    n1i=invertebrates_uncaged_n, n2i=invertebrates_caged_n, 
                                    data=data, slab=paste(last_name, year_started, location, site, sep=", "))

invertebrates_effect_size.2 <- invertebrates_effect_size.1 %>% select(c('unique_ID', 'paper', 'unique_ID_site', 'study_num', 'cluster_ID', 'inverts_cluster_ID', 'yi','vi',"herbivore_biomass_gm2","study_duration_mm"))

invertebrates_effect_size <- invertebrates_effect_size.2 %>% 
        subset(!is.na(yi))%>%
  mutate(esid=row_number())
```




# (3) Models


### Coral
```{r}
#### Multilevel model ####
##########################
# Random effects model 
coral.multi <- rma.mv(yi, vi, random = ~ 1 | paper/esid, data = coral_effect_size, slab = paper)
summary(coral.multi)
# sigma 2.1= between paper heterogeneity
# sigma 2.2= within paper heterogeneity

# apply cluster robust inference methods 
robust(coral.multi, cluster=paper, clubSandwich=TRUE)

# with herbivore biomass as a predictor
summary(rma.mv(yi, vi, mods= ~ herbivore_biomass_gm2, random = ~ 1 | paper/esid, data = coral_effect_size, slab = paper))


# with MPA as a predictor
summary(rma.mv(yi, vi, mods= ~ MPA_paper, random = ~ 1 | paper/esid, data = coral_effect_size, slab = paper))






#### Forest Plot ####
#####################
# turn 'dat' into an 'escalc' object (and add study labels)
class(coral_effect_size) # dataframe

coral.escalc <- escalc(measure="SMD", yi=yi, vi=vi, 
               data=coral_effect_size)
class(coral.escalc) # escalc

# Plot this model with aggregated data (one outcome per study)
agg <- aggregate(coral.escalc, cluster=paper, V=vcov(coral.multi, type="obs"), addk=TRUE)

res <- rma(yi, vi, method="EE", data=agg, digits=3)
res
# same results as the multilevel model above

forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-2, slab=paper)
text(-2, res$k+2, "Estimates", font=2)

# Supp Figure
png("../figures/coral-agg.png",width = 850, height = 600) 
forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-2, slab=paper, cex=1.5)
text(-2, res$k+2, "Estimates", font=2, cex=1.5)
title(main="Coral",cex.main=1.5,font=2)
dev.off()
```




### Algae
Combined ALGAE and macroalgae into one dataframe
```{r}
#### Combine the data #####
###########################
dim(ALGAE_effect_size) #20  5
dim(macroalgae_effect_size) #60  6

full_algae_effect_size <- bind_rows(ALGAE_effect_size,macroalgae_effect_size)
dim(full_algae_effect_size) #80  10


#### Multilevel model ####
##########################
# Random effects model 
algae.multi <- rma.mv(yi, vi, random = ~ 1 | paper/esid, data = full_algae_effect_size, slab = paper)
summary(algae.multi)


# apply cluster robust inference methods 
robust(algae.multi, cluster=paper, clubSandwich=TRUE)


# with herbivore biomass as a predictor
summary(rma.mv(yi, vi, mods= ~ herbivore_biomass_gm2, random = ~ 1 | paper/esid, data = full_algae_effect_size,slab = paper)) # not significant



#### Forest Plot ####
#####################
### turn 'dat' into an 'escalc' object (and add study labels)
algae.escalc <- escalc(measure="SMD", yi=yi, vi=vi, 
               data=full_algae_effect_size)
class(algae.escalc) # escalc


# Plot this model with aggregated data (one outcome per study)
agg <- aggregate(algae.escalc, cluster=paper, V=vcov(algae.multi, type="obs"), addk=TRUE)
View(agg)

res <- rma(yi, vi, method="EE", data=agg, digits=3)
res
# same results as the multilevel model above

forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-8, slab=paper)
text(-2, res$k+2, "Estimates", font=2)

# Supp Figure
png("../figures/algae-agg.png",width = 850, height = 900) 
forest(res, mlab="Pooled Estimate", 
       header=TRUE, ilab=ki, ilab.xpos=-8, 
       slab= paper, cex=1.5,xlab="Standardized Mean Difference")
title("Algae", font=2, cex.main=1.5)
text(-8, 29, "Estimates", font=2, cex=1.5)
dev.off()

```



### Turf
```{r}
#### Multi-level model #####
###########################
turf.multi <- rma.mv(yi, vi, random = ~ 1 | paper/esid, data = turf_effect_size, slab = paper)
summary(turf.multi)

# apply cluster robust inference methods 
robust(turf.multi, cluster=paper, clubSandwich=TRUE)





#### Forest Plot ####
#####################
# Plot this model with aggregated data (one outcome per study)
### turn 'dat' into an 'escalc' object (and add study labels)
turf.escalc <- escalc(measure="SMD", yi=yi, vi=vi, 
               data=turf_effect_size)
class(turf.escalc) # escalc

agg <- aggregate(turf.escalc, cluster=paper, V=vcov(turf.multi, type="obs"), addk=TRUE)
View(agg)

res <- rma(yi, vi, method="EE", data=agg, digits=3)
res
# same results as the multilevel model above

forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-2, slab=paper)
text(-2, res$k+2, "Estimates", font=2)

# supp figure
png("../figures/turf-agg.png",width = 890, height = 600) 
forest(res,mlab="Pooled Estimate", header=TRUE, ilab=ki,ilab.xpos=-10, slab=paper, cex=1.5)
title("Turf", font=2, cex.main=1.5)
text(-10, 15, "Estimates", font=2, cex=1.5)
dev.off()

```


### CCA
```{r}
#### Multi-level model #####
###########################
cca.multi <- rma.mv(yi, vi, random = ~ 1 | paper/esid, data = CCA_effect_size, slab = paper)
summary(cca.multi)

# apply cluster robust inference methods 
robust(cca.multi, cluster=paper, clubSandwich=TRUE)



#### Forest Plot ####
#####################
# Plot this model with aggregated data (one outcome per study)
### turn 'dat' into an 'escalc' object (and add study labels)
cca.escalc <- escalc(measure="SMD", yi=yi, vi=vi, 
               data=CCA_effect_size)
class(cca.escalc) # escalc

agg <- aggregate(cca.escalc, cluster=paper, V=vcov(cca.multi, type="obs"), addk=TRUE)

res <- rma(yi, vi, method="EE", data=agg, digits=3)
res
# same results as the multilevel model above

forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-2, slab=paper)
text(-2, res$k+2, "Estimates", font=2)



# supp figure
png("../figures/cca-agg.png",width = 890, height = 600) 
forest(res,mlab="Pooled Estimate", header=TRUE, ilab=ki,ilab.xpos=-4, slab=paper, cex=1.5)
title("CCA", font=2, cex.main=1.5)
text(-4, 11, "Estimates", font=2, cex=1.5)
dev.off()
```



### Invertebrates
```{r}
#### Multilevel model ####
#####################
inv.multi <- rma.mv(yi, vi, random = ~ 1 | paper/esid, data = invertebrates_effect_size,slab = paper)
summary(inv.multi)

# apply cluster robust inference methods 
robust(inv.multi, cluster=paper, clubSandwich=TRUE)





#### Forest Plot ####
#####################
# Plot this model with aggregated data (one outcome per study)
### turn 'dat' into an 'escalc' object (and add study labels)
inv.escalc <- escalc(measure="SMD", yi=yi, vi=vi, 
               data=invertebrates_effect_size)
class(inv.escalc) # escalc

agg <- aggregate(inv.escalc, cluster=paper, V=vcov(inv.multi, type="obs"), addk=TRUE)

res <- rma(yi, vi, method="EE", data=agg, digits=3)
res
# same results as the multilevel model above

forest(res, mlab="Pooled Estimate", header=TRUE, ilab=ki, ilab.xpos=-9, slab=paper)
text(-2, res$k+2, "Estimates", font=2)



# supp figure
png("../figures/inv-agg.png",width = 890, height = 600) 
forest(res,mlab="Pooled Estimate", header=TRUE, ilab=ki,ilab.xpos=-9, slab=paper, cex=1.5)
title("Invertebrates", font=2, cex.main=1.5)
text(-9, 9, "Estimates", font=2, cex=1.5)
dev.off()
```







# (4) Figures

Pooled estimates figure
```{r}
coral <- coef(summary(coral.multi)) %>%
        mutate(Taxa = "Coral") %>%
        mutate(Significance= "No")

algae <- coef(summary(algae.multi))%>%
        mutate(Taxa = "Algae")%>%
        mutate(Significance= "Yes")

turf <- coef(summary(turf.multi))%>%
        mutate(Taxa = "Turf")%>%
        mutate(Significance= "No")

cca <- coef(summary(cca.multi))%>%
        mutate(Taxa = "CCA")%>%
        mutate(Significance= "Yes")

inv <- coef(summary(inv.multi))%>%
        mutate(Taxa = "Invertebrates")%>%
        mutate(Significance= "No")

plot.df <- rbind(coral, algae, turf, cca, inv)

plot.df$Taxa <- factor(plot.df$Taxa, levels = c("Invertebrates", "Turf","CCA", "Algae", "Coral"))


p_pooled.estimates <- ggplot(plot.df, aes(y=Taxa, x=estimate, colour=Significance)) +
        geom_pointrange(aes(xmin=ci.lb, xmax=ci.ub), size=1) +
        theme_pubr(base_size=16) +
        geom_vline(xintercept = 0, linetype="dashed")+
        scale_colour_manual(values=c("darkgrey","black")) +
  labs(x="Standardized Mean Difference")
p_pooled.estimates

ggsave(p_pooled.estimates, filename="../figures/pooled-estimates.png", height=6, width=8)
```

