---
title: "Fish Surveys at Tile Sites"
author: "Jamie McDevitt-Irwin"
date: "2/15/2022"
output: html_document
---

Dependencies: You need to run dovs-data-cleaning-v2.Rmd

**Tiles Site Dovs**
Egmont il lubine- BIOT_7097_DOV_2_Egmont_20190318
Egmont il de rats- BIOT_7097_DOV_1_Egmont_20190317
Middle brother- BIOT_7097_DOV_3_Middle Brother_2019
Nelson- BIOT_7097_DOV_4_NelsonsIsland_2018
Salomon lagoon- BIOT_7097_DOV_6_Salomon_N_20190311
Salomon seaward- BIOT_7097_DOV_5_Salomon_S_20190310
Peros Banos lagoon- BIOT_7097_DOV_7_PerosBanhos_Lagoon_20190303
Peros Banos seaward- BIOT_7097_DOV_8_PerosBanhos_Middle_2018


# Libraries
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse);library(ggpubr);library(reshape2);library(stringr);library(vegan);library(plotly);library(linguisticsdown);library(lme4);library(indicspecies);library(janitor);library(ade4);library(picante);library(FD);library(mvabund);library(cowplot);library(glmmTMB);library(ggeffects)
```



# Create Data
```{r}
#### SPECIES LEVEL #####
# Filter out tile sites
unique(dovs.wide$OpCode)

dovs.wide.tiles <- dovs.wide %>%
  # filter out opcodes only for our eight tile sites 
  filter(OpCode %in% c("BIOT_7097_DOV_2_Egmont_20190318",
                                   "BIOT_7097_DOV_1_Egmont_20190317",
                                   "BIOT_7097_DOV_3_Middle Brother_2019",
                                   "BIOT_7097_DOV_4_NelsonsIsland_2018",
                                   "BIOT_7097_DOV_6_Salomon_N_20190311",
                                   "BIOT_7097_DOV_5_Salomon_S_20190310",
                                   "BIOT_7097_DOV_7_PerosBanhos_Lagoon_20190303",
                                   "BIOT_7097_DOV_8_PerosBanhos_Middle_2018")) %>%
    # make a new column for each our our tiles sites
  
  mutate(Tile.Site = ifelse(OpCode == "BIOT_7097_DOV_2_Egmont_20190318", "Il Lubine",
                            ifelse(OpCode == "BIOT_7097_DOV_1_Egmont_20190317", "Il de rats",
                                   ifelse(OpCode == "BIOT_7097_DOV_4_NelsonsIsland_2018", "Nelson",
                                   ifelse(OpCode == "BIOT_7097_DOV_3_Middle Brother_2019", "Middle Brother",
                                          ifelse(OpCode == "BIOT_7097_DOV_6_Salomon_N_20190311", "Salomon lagoon",
                                                 ifelse(OpCode == "BIOT_7097_DOV_5_Salomon_S_20190310", "Salomon seaward",
                                                        ifelse(OpCode == "BIOT_7097_DOV_7_PerosBanhos_Lagoon_20190303", "Peros Banhos Lagoon", "Peros Banhos Seaward")))))))) %>%
  relocate(Tile.Site, .after= Site)%>% 
  # get rid of any species that have all zeros
select_if(~ !is.numeric(.) || sum(.) != 0)

dim(dovs.wide.tiles) # 31 184







# Long Version
dovs.long.tiles <- dovs.wide.tiles %>%
  pivot_longer(-c(Atoll:OpCode_transect, Shark_Abundance, Shark_Sum_Abundance), 
               names_to= "Full.Species.Name", values_to = "Count") %>%
  # add in family
  mutate(Family= word(Full.Species.Name, 1)) %>%
  relocate(Family, .before= Full.Species.Name)


save(dovs.wide.tiles, file="../data/created/dovs.wide.tiles.Rdata")







#### FAMILY LEVEL #####
# Family Level Data
dovs.wide.tiles.family <- dovs.wide.family %>%
  # filter out opcodes only for our eight tile sites 
  filter(OpCode %in% c("BIOT_7097_DOV_2_Egmont_20190318",
                                   "BIOT_7097_DOV_1_Egmont_20190317",
                                   "BIOT_7097_DOV_3_Middle Brother_2019",
                                   "BIOT_7097_DOV_4_NelsonsIsland_2018",
                                   "BIOT_7097_DOV_6_Salomon_N_20190311",
                                   "BIOT_7097_DOV_5_Salomon_S_20190310",
                                   "BIOT_7097_DOV_7_PerosBanhos_Lagoon_20190303",
                                   "BIOT_7097_DOV_8_PerosBanhos_Middle_2018")) %>%
    # make a new column for each our our tiles sites
  
  mutate(Tile.Site = ifelse(OpCode == "BIOT_7097_DOV_2_Egmont_20190318", "Il Lubine",
                            ifelse(OpCode == "BIOT_7097_DOV_1_Egmont_20190317", "Il de rats",
                                   ifelse(OpCode == "BIOT_7097_DOV_4_NelsonsIsland_2018", "Nelson",
                                   ifelse(OpCode == "BIOT_7097_DOV_3_Middle Brother_2019", "Middle Brother",
                                          ifelse(OpCode == "BIOT_7097_DOV_6_Salomon_N_20190311", "Salomon lagoon",
                                                 ifelse(OpCode == "BIOT_7097_DOV_5_Salomon_S_20190310", "Salomon seaward",
                                                        ifelse(OpCode == "BIOT_7097_DOV_7_PerosBanhos_Lagoon_20190303", "Peros Banhos Lagoon", "Peros Banhos Seaward")))))))) %>%
  relocate(Tile.Site, .after= Site)

dim(dovs.wide.tiles.family) # 31 17
colnames(dovs.wide.tiles.family)



# Site averages
fish.site.tiles.average <- dovs.wide.tiles.family %>%
  group_by(Tile.Site, Atoll) %>%
  # calculate the mean per tile.site (averaged across teh transects)
  summarize(Herbivores.avg = mean(Herbivores),
            Chaetodontidae.avg = mean(Chaetodontidae),
            Mesopredators.avg = mean(Mesopredators),
            corallivore.avg = mean(corallivore))
dim(fish.site.tiles.average) # 8 6
save(fish.site.tiles.average, file="../data/created/fish.site.tiles.average.RData")

# Egmont vs Brothers
# egmont= 1 and 6
# brothers= 69.5

69.5/(7/2)
```

Summaries
```{r}

unique(dovs.long.tiles$Full.Species.Name) # 174
dim(dovs.wide.tiles.family) # 31 17 (now 31 by 18 )
```



# Raw Data Plots
```{r}
# Make the data have the same x axis as the other plots
dovs.long.tiles$Tile.Site <- factor(dovs.long.tiles$Tile.Site, levels=c("Middle Brother", "Nelson", "Peros Banhos Lagoon", 
"Peros Banhos Seaward", "Salomon lagoon", "Salomon seaward", "Il de rats", "Il Lubine"))

dovs.long.tiles$Atoll <- factor(dovs.long.tiles$Atoll, levels=c("Brothers", "Nelsons Island", "Peros Banhos", 
"Salomon", "Egmont"))



# Herbivore Plot
p_herbs_relabundance <- dovs.long.tiles %>%
  filter(Family=="Scaridae" | Family == "Acanthuridae") %>%
  group_by(Tile.Site, Family) %>%
  ggplot(aes(x=Tile.Site, y=Count, fill=Family, color=Family)) +
    geom_bar(stat="identity", position= "fill") +
  theme_pubr()+
  labs(x="", y="Relative Abundance") +
  scale_x_discrete(guide = guide_axis(angle = 60),
                   labels=c("Il Lubine" = "Egmont- Ile Lubine",
                            "Il de rats" = "Egmont- Ile de rats"))
p_herbs_relabundance

ggsave(p_herbs_relabundance, height=8, width=8, file="../figures/herbivores-relative-abundance.png")


# Mesopredator Plot
p_meso_relabundance <- dovs.long.tiles %>%
  filter(Family %in% c("Lutjanidae", "Lethrinidae", "Haemulidae","Serranidae", "Carangidae")) %>%
  group_by(Tile.Site, Family) %>%
  ggplot(aes(x=Tile.Site, y=Count, fill=Family, color=Family)) +
    geom_bar(stat="identity", position= "fill") +
  theme_pubr()+
  labs(x="", y="Relative Abundance") +
  scale_x_discrete(guide = guide_axis(angle = 60),
                   labels=c("Il Lubine" = "Egmont- Ile Lubine",
                            "Il de rats" = "Egmont- Ile de rats"))
p_meso_relabundance

ggsave(p_meso_relabundance, file="../figures/mesopredator-relative-abundance.png",
       height=7, width=7)




# Prep the data so it has the same colors as the bruvs data
dovs.wide.tiles.family$Tile.Site <- factor(dovs.wide.tiles.family$Tile.Site, levels=c("Middle Brother", "Nelson", "Peros Banhos Lagoon", 
"Peros Banhos Seaward", "Salomon lagoon", "Salomon seaward", "Il de rats", "Il Lubine"))

dovs.wide.tiles.family$Atoll <- factor(dovs.wide.tiles.family$Atoll, levels=c("Brothers", "Nelsons Island", "Peros Banhos", 
"Salomon", "Egmont"))


viridis::viridis(n = 5)


# Herbivores
p_tiles.herbivores <- dovs.wide.tiles.family %>%
  group_by(Tile.Site) %>%
  mutate(Herbivore.mean= mean(Herbivores),
           Herbivore.SD = sd(Herbivores),
         Herbivore.SE = Herbivore.SD/sqrt(length(Herbivores))) %>%
  ggplot(aes(x=Tile.Site, y=Herbivore.mean, color=Atoll)) + 
  geom_point(size=6)+
  geom_errorbar(aes(ymin = Herbivore.mean - Herbivore.SD, 
                    ymax = Herbivore.mean + Herbivore.SD), 
                width=0.2) +
    theme_pubr(base_size = 16) +  
  theme(axis.text.x = element_text(angle = 90)) +
    theme(axis.text.x = element_blank())+
  ylab("Herbivores (no./150m2)") +
  xlab("")+
  scale_color_manual(values= c("#440154FF","#3B528BFF","#21908CFF","#5DC863FF","#FDE725FF")) +
  guides(col = "none")

p_tiles.herbivores

ggsave(plot= p_tiles.herbivores, file= "../figures/tiles-herbivores.png",
       height=5, width=9)
save(p_tiles.herbivores, file= "../data/tiles-herbivores.RData")




# Plot of Chaetodontidae
p_tiles.chaet <- dovs.wide.tiles.family %>%
  group_by(Tile.Site) %>%
  mutate(Chaetodontidae.mean= mean(Chaetodontidae),
           Chaetodontidae.SD = sd(Chaetodontidae),
         Chaetodontidae.SE = Chaetodontidae.SD/sqrt(length(Chaetodontidae))) %>%
  ggplot(aes(x=Tile.Site, y=Chaetodontidae.mean, color=Atoll)) + 
  geom_point(size=6)+
  geom_errorbar(aes(ymin = Chaetodontidae.mean - Chaetodontidae.SD, 
                    ymax = Chaetodontidae.mean + Chaetodontidae.SD), 
                width=0.2) +
  theme_pubr(base_size = 16) +  
  theme(axis.text.x = element_text(angle = 90)) +
    theme(axis.text.x = element_blank())+
  ylab("Corallivores (no./150m2)")  + 
    xlab("")+
    scale_color_manual(values= c("#440154FF","#3B528BFF","#21908CFF","#5DC863FF","#FDE725FF")) +
  guides(col = "none")
p_tiles.chaet

ggsave(plot= p_tiles.chaet, file= "../figures/tiles-chaetodontidae.png",
       height=5, width=9)
save(p_tiles.chaet, file= "../data/tiles-chaetodontidae.RData")




# Mesopredator abundance
p_tiles.mesopredators <- dovs.wide.tiles.family %>%
  group_by(Tile.Site) %>%
  mutate(Mesopredator.mean= mean(Mesopredators),
           Mesopredator.SD = sd(Mesopredators),
         Mesopredator.SE = Mesopredator.SD/sqrt(length(Mesopredators))) %>%
  ggplot(aes(x=Tile.Site, y=Mesopredator.mean, color=Atoll)) + 
  geom_point(size=6)+
  geom_errorbar(aes(ymin = Mesopredator.mean - Mesopredator.SD, 
                    ymax = Mesopredator.mean + Mesopredator.SD), 
                width=0.2) +
  theme_pubr(base_size = 16) +  
  theme(axis.text.x = element_text(angle = 90)) +
    theme(axis.text.x = element_blank())+
  ylab("Mesopredators (no./150m2)") +
    xlab("")+
    scale_color_manual(values= c("#440154FF","#3B528BFF","#21908CFF","#5DC863FF","#FDE725FF")) +
  guides(col = "none")
p_tiles.mesopredators

ggsave(plot= p_tiles.mesopredators, file= "../figures/tiles-mesopredators.png",
       height=5, width=9)
save(p_tiles.mesopredators, file= "../data/tiles-mesopredators.RData")

```





# Shark-Fish Plots
```{r}
##########
# Herbivores
##########
p_herbivores <- dovs.wide.tiles.family %>%
  ggplot(aes(x=Shark_Sum_Abundance, y=Herbivores)) + 
  geom_point(size=3) +
  geom_smooth(method="lm") +
  theme_pubr()+
  theme(legend.position= 'none',
        axis.title.y = element_blank(),
        axis.text.y = element_text(size=26),
        axis.title.x= element_text(size=28),
        axis.text.x= element_text(size=26),
        title= element_text(size=28)) +
  xlab("Shark Abundance")
p_herbivores


###########
# Corallivores
###########
# Butterflyfish
dovs.wide.tiles.family %>%
  ggplot(aes(x=Shark_Sum_Abundance, y=Chaetodontidae)) + 
  geom_point(size=3) +
  geom_smooth(method="lm")+
  ylab("Chaetodontidae (no./150m2)") +
  theme_pubr() +
  ylim(0,25) +
  ggtitle("Chaetodontidae")








###########
# Mesopredators
###########

dovs.wide.tiles.family %>%
  ggplot(aes(x=Shark_Sum_Abundance, y=Mesopredators)) + 
  geom_point(size=3) +
  geom_smooth(method="lm")+
  theme_pubr()+
  theme(legend.position= 'none',
        axis.title.y = element_blank(),
        axis.text.y = element_text(size=24),
        axis.title.x= element_text(size=26),
        axis.text.x= element_text(size=24),
        title= element_text(size=24)) +
  labs(x="Shark Abundance")

```




# Models
nbinom2() is the defult for negative binomial in most packages.
https://stats.stackexchange.com/questions/284911/type-i-and-type-ii-negative-binominal-distribution-in-zero-inflated-negative-bin


Count data! --> poisson or negative binomial distribution, seeing what fits best
```{r}

####### Mesopredators #######
#############################
hist(dovs.wide.tiles.family$Mesopredators) # super wierd distribution

m1 <- glmmTMB(Mesopredators ~ Shark_Sum_Abundance + (1|OpCode_Site), data=dovs.wide.tiles.family, family = poisson)

m2 <- glmmTMB(Mesopredators ~ Shark_Sum_Abundance + (1|OpCode_Site), data=dovs.wide.tiles.family, family = nbinom2())

AIC(m1)
AIC(m2) # best model

summary(m2) # significant
performance::r2(m2)  


# Model Fit
library(DHARMa)
simres <- simulateResiduals(m2)
plot(simres) # slight issue, but overall mainly looks ok?


# Pull out the coefficients and SE for plotting
coefs <- as.data.frame((summary(m2)$coefficients)$cond) %>%
  rownames_to_column() %>%
  rename(Std.Error = "Std. Error") %>% 
  rename(p.val = "Pr(>|z|)") %>%
  mutate(Color = ifelse(p.val < 0.059, "black", "dark grey"))%>%
  filter(rowname != "(Intercept)")

p_model_meso <- ggplot(coefs, aes(x=Estimate, y=rowname, color=Color)) +
  geom_point(size=5) +
  geom_errorbar(aes(xmin=Estimate-Std.Error, xmax=Estimate+Std.Error), width=.2,
                 position=position_dodge(0.05)) + 
  theme_pubr(base_size = 16) +
  geom_vline(xintercept=0,linetype=2) +
  labs(y="", x="Mesopredators")+
  scale_color_identity()

p_model_meso

# Prediction Plots
meso.df <- as.data.frame(ggemmeans(m2, c("Shark_Sum_Abundance")))

p_meso.predict <- ggplot(meso.df, aes(x, predicted)) + 
  geom_line(size=1.5) +
  theme_pubr(base_size=16) +
  labs(x="Shark Abundance", y="Predicted Mesopredators") + 
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.1, colour=NA) +
  geom_text(label="*", x=6.5, y=50, size=10) +
  ggtitle("a)")
p_meso.predict





####### Herbivores #######
#############################
hist(dovs.wide.tiles.family$Herbivores)

m1 <- glmmTMB(Herbivores ~ Shark_Sum_Abundance + Mesopredators + (1|OpCode_Site), data=dovs.wide.tiles.family, family = poisson)
# NAN

m2 <- glmmTMB(Herbivores ~ Shark_Sum_Abundance + Mesopredators + (1|OpCode_Site), data=dovs.wide.tiles.family, family = nbinom2())

AIC(m1)
AIC(m2) # only one that works

summary(m2)

summary(m2) # not significant
performance::r2(m2)
# Conditional R2: 0.629
#      Marginal R2: 0.009
     
# Model Fit
library(DHARMa)
simres <- simulateResiduals(m2)
plot(simres) # has one issue, but overall looks ok



# Pull out the coefficients and SE for plotting
coefs <- as.data.frame((summary(m2)$coefficients)$cond) %>%
  rownames_to_column() %>%
  rename(Std.Error = "Std. Error") %>% 
  rename(p.val = "Pr(>|z|)") %>%
  mutate(Color = ifelse(p.val < 0.059, "black", "dark grey"))%>%
  filter(rowname != "(Intercept)")

p_model_herbs <- ggplot(coefs, aes(x=Estimate, y=rowname, color=Color)) +
  geom_point(size=5) +
  geom_errorbar(aes(xmin=Estimate-Std.Error, xmax=Estimate+Std.Error), width=.2,
                 position=position_dodge(0.05)) + 
  theme_pubr(base_size = 16) +
  geom_vline(xintercept=0,linetype=2) +
  labs(y="", x="Herbivores")+
  scale_color_identity()
p_model_herbs



# Prediction Plots
herb.shark.df <- as.data.frame(ggemmeans(m2, c("Shark_Sum_Abundance")))
herb.meso.df <- as.data.frame(ggemmeans(m2, c("Mesopredators")))

p_herb.shark.predict <- ggplot(herb.shark.df, aes(x, predicted)) + 
  geom_line(size=1.5) +
  theme_pubr(base_size=16) +
  labs(x="", y="Predicted Herbivores") + 
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.1, colour=NA)+
  ggtitle("b)")
p_herb.shark.predict


p_herb.meso.predict <- ggplot(herb.meso.df, aes(x, predicted)) + 
  geom_line(size=1.5) +
  theme_pubr(base_size=16) +
  labs(x="", y="") + 
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.1, colour=NA)+
  ggtitle("c)")
p_herb.meso.predict

p_herbivores.predict <- ggarrange(p_herb.shark.predict, p_herb.meso.predict)
p_herbivores.predict

###### Chaetodontidae ########
########################
hist(dovs.wide.tiles.family$Chaetodontidae)

m1 <- glmmTMB(Chaetodontidae ~ Shark_Sum_Abundance + Mesopredators + (1|OpCode_Site), data=dovs.wide.tiles.family, family = poisson)

m2 <- glmmTMB(Chaetodontidae ~ Shark_Sum_Abundance + Mesopredators + (1|OpCode_Site), data=dovs.wide.tiles.family, family = nbinom2())

AIC(m1)
AIC(m2)# best model

summary(m2) # not significant
performance::r2(m2)
  # Conditional R2: 0.372
  #    Marginal R2: 0.063

# Model Fit
library(DHARMa)
simres <- simulateResiduals(m2)
plot(simres) # one minor issue? 



# Pull out the coefficients and SE for plotting
coefs <- as.data.frame((summary(m2)$coefficients)$cond) %>%
  rownames_to_column() %>%
  rename(Std.Error = "Std. Error") %>% 
  rename(p.val = "Pr(>|z|)") %>%
  mutate(Color = ifelse(p.val < 0.059, "black", "dark grey"))%>%
  filter(rowname != "(Intercept)")

p_model_corallivores <- ggplot(coefs, aes(x=Estimate, y=rowname, color=Color)) +
  geom_point(size=5) +
  geom_errorbar(aes(xmin=Estimate-Std.Error, xmax=Estimate+Std.Error), width=.2,
                 position=position_dodge(0.05)) + 
  theme_pubr(base_size = 16) +
  geom_vline(xintercept=0,linetype=2) +
  labs(y="", x="Corallivores")+
  scale_color_identity()
  
p_model_corallivores

# Prediction Plots
coral.shark.df <- as.data.frame(ggemmeans(m2, c("Shark_Sum_Abundance")))
coral.meso.df <- as.data.frame(ggemmeans(m2, c("Mesopredators")))

p_coral.shark.predict <- ggplot(coral.shark.df, aes(x, predicted)) + 
  geom_line(size=1.5) +
  theme_pubr(base_size=16) +
  labs(x="", y="Predicted Corallivores") + 
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.1, colour=NA)+
  ggtitle("d)")
p_coral.shark.predict


p_coral.meso.predict <- ggplot(coral.meso.df, aes(x, predicted)) + 
  geom_line(size=1.5) +
  theme_pubr(base_size=16) +
  labs(x="", y="") + 
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high), alpha=0.1, colour=NA) +
  ggtitle("e)")
p_coral.meso.predict

p_corallivore.predict <- ggarrange(p_coral.shark.predict, p_coral.meso.predict)
p_corallivore.predict

model_fish <- ggarrange(p_model_meso, 
          p_model_herbs, 
          p_model_corallivores, 
          ncol=1, nrow=3)
model_fish

ggsave(model_fish, file="../figures/model-fishes.png",
       height=8, width=9)



load("../../grazing/data/bites-predict.RData") # p_bites.predict





model_fish.predictions <- ggarrange(p_meso.predict, 
          p_herbivores.predict, 
          p_corallivore.predict, 
          p_bites.predict,
          ncol=1, nrow=4)
model_fish.predictions


ggsave(model_fish.predictions, file="../figures/model-fishes-predictions.png",
       height=13, width=7)

```

Looks good! 6April2023
