---
title: 'Tile Corals: Analysis'
author: "Jamie McDevitt-Irwin"
date: "2/2/2022"
output: html_document
---

Dependancy: tiles-corals-data-cleaning.Rmd


# Packages
```{r}
library(lme4)
library(lattice)
library(MASS)
require(pscl) # alternatively can use package ZIM for zero-inflated models
library(lmtest)
library(GLMMadaptive) # mixed models that are zero inflated 
library(glmmTMB)
library(lsmeans)
library(DHARMa)
library(dplyr)

#devtools::install_github("mtorchiano/effsize")
library(effsize)
library(piecewiseSEM)

library(devtools)
#install_github("jslefche/piecewiseSEM@devel", build_vignette = TRUE)

```


# Plots
```{r}
############
# Overall Corals
############
meancorals.treatment <- corals.2021_long %>%
  group_by(Treatment) %>%
  summarise(sum= sum(Coral), 
            mean=mean(Coral), 
            se=std.error(Coral))
meancorals.treatment

p_overall <- meancorals.treatment %>% ggplot(aes(x= Treatment, y=mean)) +
  geom_bar(position = "dodge", stat='identity')+
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(.9)) +
  labs(y="Coral abundance (mean +/- se)") +
  theme_pubr(base_size= 16) +
  theme(legend.position = "right")
p_overall

ggsave(file= "../figures/overall.png",
       plot=p_overall,
       height= 7,
       width= 10)

############
# Overall- Tile Position
############
meancorals <- corals.2021_long %>%
  group_by(Treatment, Tile_position) %>%
  summarise(sum= sum(Coral), 
            mean=mean(Coral), 
            se=std.error(Coral)) %>%
  mutate_if(is.character, as.factor) %>%
    mutate(Tile_position=fct_relevel(Tile_position,c("Top","Bottom","Side")))


library(viridis)
p_corals <- meancorals %>% ggplot(aes(x= Treatment, y=mean, fill= Tile_position)) +
  geom_bar(position = "dodge", stat='identity')+
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(.9)) +
  labs(y="Coral abundance (mean +/- se)", fill= "Tile Position") +
  theme_pubr(base_size= 16) +
  theme(legend.position = "right") + 
  scale_fill_viridis(discrete=TRUE)
p_corals

ggsave(file= "../figures/overall-corals.png",
       plot=p_corals,
       height= 7,
       width= 10)
  



############
# By Site
############
meancorals <- corals.2021_long %>%
  group_by(Site, Treatment) %>%
  summarise(sum= sum(Coral), 
            mean=mean(Coral), 
            se=std.error(Coral))

p_coralsXsite <- meancorals %>% 
  ggplot(aes(x= Treatment, y=mean)) +
  geom_bar(position = "dodge", stat='identity')+
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(.9)) +
  theme_pubr() + 
  facet_wrap(~ Site)

p_coralsXsite

ggsave(file= "../figures/coralsXsite.pdf",
       plot=p_coralsXsite,
       height= 7,
       width= 9)


############
# By Site- Position
############
meancorals <- corals.2021_long %>%
  group_by(Site, Treatment, Tile_position) %>%
  summarise(sum= sum(Coral), 
            mean=mean(Coral), 
            se=std.error(Coral))

p_coralsXsite <- meancorals %>% 
  ggplot(aes(x= Treatment, y=mean, fill= Tile_position)) +
  geom_bar(position = "dodge", stat='identity')+
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(.9)) +
  theme_pubr() + 
  facet_wrap(~ Site)

p_coralsXsite

ggsave(file= "../figures/coralsXsiteXposition.pdf",
       plot=p_coralsXsite,
       height= 7,
       width= 9)



############
# Coral Size
############
corals.2021 %>%
  group_by(Treatment, Coral_size_bin) %>%
  count()


corals.2021 %>% ggplot(aes(x= Treatment, fill=Coral_size_bin)) +
  geom_bar(position="fill") +  
  theme_pubr(base_size= 16) +
  theme(legend.position = "right")

```
Not really a difference in size between treatments! (a few corals dont have size here though)

Final coral recruit plots
- decided to plot these with raw data instead of lsmeans because of some confusion when people looked at the means
```{r}
# Overall 
colnames(corals.2021_wide)
meancorals.overall <- corals.2021_wide %>%
  group_by(Treatment) %>%
  summarise(sum= sum(All.Corals), 
            mean=mean(All.Corals), 
            se=std.error(All.Corals)) 

p_corals_overall <- ggplot(meancorals.overall, aes(x=Treatment, y=mean, col=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax= mean+se)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("a) Overall")+ 
    scale_colour_hue(h = c(180, 300))
p_corals_overall


# Top
colnames(corals.2021_wide)
meancorals.top <- corals.2021_wide %>%
  group_by(Treatment) %>%
  summarise(sum= sum(Top), 
            mean=mean(Top), 
            se=std.error(Top)) 

p_corals_top <- ggplot(meancorals.top, aes(x=Treatment, y=mean, col=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax= mean+se)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("b) Top")+ 
    scale_colour_hue(h = c(180, 300)) +
  geom_text(label="*", x=3.2, y=0.6, size=10, color="black")

p_corals_top

# Bottom
colnames(corals.2021_wide)
meancorals.bottom <- corals.2021_wide %>%
  group_by(Treatment) %>%
  summarise(sum= sum(Bottom), 
            mean=mean(Bottom), 
            se=std.error(Bottom)) 

p_corals_bottom <- ggplot(meancorals.bottom, aes(x=Treatment, y=mean, col=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax= mean+se)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("c) Bottom")+ 
    scale_colour_hue(h = c(180, 300)) +
  geom_text(label="*", x=3.2, y=0.45, size=10, color="black") 

p_corals_bottom


# Side
colnames(corals.2021_wide)
meancorals.side <- corals.2021_wide %>%
  group_by(Treatment) %>%
  summarise(sum= sum(Side), 
            mean=mean(Side), 
            se=std.error(Side)) 

p_corals_side <- ggplot(meancorals.side, aes(x=Treatment, y=mean, col=Treatment)) +
  geom_pointrange(aes(ymin=mean-se, ymax= mean+se)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("d) Side")+ 
    scale_colour_hue(h = c(180, 300))
p_corals_side




test <- ggarrange(p_corals_top, 
          p_corals_side, 
          p_corals_bottom)
test

p_coral <- ggarrange(p_corals_overall, test, 
                     ncol=2, common.legend=TRUE,
                     widths=c(2,3))
p_coral
ggsave(p_coral, file="../figures/coral-means.png",
       height=5, width=10)

save(p_coral, file="../data/created-data/coral-means.RData")
```



# Models
## Overall
https://stats.stackexchange.com/questions/531601/dharma-quantile-deviations-detected 
```{r}
# How much of the data is zero?
100*sum(corals.2021_wide$All.Corals == 0)/nrow(corals.2021_wide) # 65.25822
hist(corals.2021_wide$All.Corals) # very zero inflated

# Convert characters to factors 
corals.2021_wide$Treatment <- as.factor(corals.2021_wide$Treatment)
corals.2021_wide$Island <- as.factor(corals.2021_wide$Island)
corals.2021_wide$Transect <- as.factor(corals.2021_wide$Transect)
corals.2021_wide$Tile <- as.factor(corals.2021_wide$Tile)
corals.2021_wide$Tile_Treatment <- as.factor(corals.2021_wide$Tile_Treatment)
corals.2021_wide$Site <- as.factor(corals.2021_wide$Site)



#### Initial Models ####
m1 <- glmmTMB::glmmTMB(All.Corals ~ Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = poisson)

m2 <- glmmTMB(All.Corals ~ Treatment + (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = poisson)

m3 <- glmmTMB(All.Corals ~ Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = nbinom2())

m4 <- glmmTMB(All.Corals ~ Treatment + (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = nbinom2())


AIC(m1,m2,m3,m4) # m2 is best

summary(m2)
performance::r2(m2)  
# Conditional R2: 0.395
#      Marginal R2: 0.023
# Had to decrease the random effects structure to get an R2 value for conditional

car::Anova(m2, type=2) # not significant
#            Chisq Df Pr(>Chisq)
# Treatment 3.5915  2      0.166

# Check residuals
simres <- simulateResiduals(m2)
plot(simres) # all good

# Plot
overall.em <- emmeans(m2, ~ Treatment, type="response")
overall.em.df <- as.data.frame(overall.em)

p_eemeans_overall <- ggplot(overall.em.df, aes(x=Treatment, y=rate, color=Treatment)) +
  geom_pointrange(size=1, aes(ymin=rate-SE, ymax= rate+SE)) +
  theme_pubr(base_size=16) +
  labs(y="Coral Recruits (least square means)") +
  ggtitle("a) Overall") + 
    scale_colour_hue(h = c(180, 300)) 
p_eemeans_overall

ggsave(p_eemeans_overall, file="../figures/corals-eemeans.png")
```

Overall, we find no difference in coral recruit numbers between our treatments (caged, uncaged and partially caged)



### Top
```{r}
# How much of the data is zero?
100*sum(corals.2021_wide$Top == 0)/nrow(corals.2021_wide) # 87.32394
hist(corals.2021_wide$Top) # very zero inflated



#### Initial Models ####
m1 <- glmmTMB(Top ~  Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = poisson)

m2 <- glmmTMB(Top ~  Treatment + (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = poisson)

m3 <- glmmTMB(Top ~  Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = nbinom2())

m4 <- glmmTMB(Top ~  Treatment + (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = nbinom2())


AIC(m1,m2,m3,m4) #m1 is best

summary(m1)
performance::r2(m1)
# same warnings as above
# 
#   Conditional R2: 0.572
#      Marginal R2: 0.209

car::Anova(m1, type=2) 
# Analysis of Deviance Table (Type II Wald chisquare tests)
# 
# Response: Coral
#            Chisq Df Pr(>Chisq)    
# Treatment 16.153  2  0.0003108 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

# Model diagnostics
m1_simresids <- simulateResiduals(m1)
plot(m1_simresids) # no significant deviations

# Plot
top.em <- emmeans(m1, ~ Treatment, type="response")
pairs(top.em)
top.em.df <- as.data.frame(top.em)

p_eemeans_top <- ggplot(top.em.df, aes(x=Treatment, y=rate, color=Treatment)) +
  geom_pointrange(aes(ymin=rate-SE, ymax= rate+SE)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("b) Top")+
  geom_text(label="*", x=3.2, y=0.2, size=10, color="black") +
  scale_colour_hue(h = c(180, 300)) 
p_eemeans_top

ggsave(p_eemeans_top, file="../figures/corals-eemeans-top.png")

```

Treatment is very significant when just looking at corals found on the top of the tile, with the caged tiles having significantly more corals than the uncaged tiles.

### Bottom
```{r}
# How much of the data is zero?
100*sum(corals.2021_wide$Bottom == 0)/nrow(corals.2021_wide) # 80.28169
hist(corals.2021_wide$Bottom) # very zero inflated


# Initial Models
m5 <- glmmTMB(Bottom ~ Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = poisson)

m6 <- glmmTMB(Bottom ~ Treatment+ (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = poisson)

m7 <- glmmTMB(Bottom ~ Treatment + (1|Site) + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = nbinom2())

m8 <- glmmTMB(Bottom ~ Treatment+ (1|Site) + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = nbinom2())
# doesn't converge

AIC(m5,m6,m7,m8) # m6 

# Model Diagnostics
m6_simresids <- simulateResiduals(m6)
plot(m6_simresids) # all good

performance::r2(m6)
 # Conditional R2: 0.354
 #     Marginal R2: 0.066

car::Anova(m6, type=2)
# Response: Coral
#           Chisq Df Pr(>Chisq)  
# Treatment 7.123  2     0.0284 *

# Plot
bottom.em <- emmeans(m6, ~ Treatment, type="response")
pairs(bottom.em)
bottom.em.df <- as.data.frame(bottom.em)

p_eemeans_bottom <- ggplot(bottom.em.df, aes(x=Treatment, y=rate, col=Treatment)) +
  geom_pointrange(aes(ymin=rate-SE, ymax= rate+SE)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="") + 
  ggtitle("c) Bottom")+ 
    scale_colour_hue(h = c(180, 300)) +
  geom_text(label="*", x=3.2, y=0.55, size=10, color="black")

p_eemeans_bottom

ggsave(p_eemeans_bottom, file="../figures/corals-eemeans-bottom.png")

```

### Side
```{r}
# How much of the data is zero?
100*sum(corals.2021_wide$Side == 0)/nrow(corals.2021_wide) #91.07981
hist(corals.2021_wide$Side) # very zero inflated


# Initial Models
m5 <- glmmTMB(Side ~ Treatment + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = poisson)

m6 <- glmmTMB(Side ~ Treatment+ (1|Tile), zi = ~ 1, data = corals.2021_wide, family = poisson)

m7 <- glmmTMB(Side ~ Treatment + (1|Tile), zi = ~ 0, data = corals.2021_wide, family = nbinom2())

m8 <- glmmTMB(Side ~ Treatment + (1|Tile), zi = ~ 1, data = corals.2021_wide, family = nbinom2())
# convergence issue

AIC(m5,m6,m7,m8) # m7 is barely better? but it doesn't give you an R2 for random effects, so we go with m4 since its simpler and close in AIC


summary(m7)
summary(m5)
performance::r2(m7) # random effects errors --> singular 
performance::r2(m5)
# Conditional R2: 0.370
#      Marginal R2: 0.012
# Had to take away site to get a value for random effects R2 (tells you to respecify random structure)


summary(m5)
performance::r2(m5)
# Conditional R2: 0.370
#      Marginal R2: 0.012

# Model Diagnostics
m5_simresids <- simulateResiduals(m5)
plot(m5_simresids) # all good


car::Anova(m5, type=2)
# not significant



# Plot
side.em <- emmeans(m5, ~ Treatment, type="response")
side.em.df <- as.data.frame(side.em)

p_eemeans_side <- ggplot(side.em.df, aes(x=Treatment, y=rate, col=Treatment)) +
  geom_pointrange(aes(ymin=rate-SE, ymax= rate+SE)) +
  theme_pubr(base_size=16) +
  theme(axis.text.x = element_blank(),
        legend.position="none") +
  labs(y="", x="") + 
  ggtitle("d) Side")+ 
    scale_colour_hue(h = c(180, 300))
p_eemeans_side

ggsave(p_eemeans_side, file="../figures/corals-eemeans-side.png")


```

### Plot
```{r}
ggarrange(p_eemeans_overall, 
          p_eemeans_top, 
          p_eemeans_side, 
          p_eemeans_bottom)

test <- ggarrange(p_eemeans_top, 
          p_eemeans_side, 
          p_eemeans_bottom)


p_coral <- ggarrange(p_eemeans_overall, test, 
                     ncol=2, common.legend=TRUE,
                     widths=c(2,3))
p_coral
ggsave(p_coral, file="../figures/coral-eemeans.png",
       height=5, width=10)

save(p_coral, file="../data/created-data/coral-eemeans.RData")

```



# Effect Sizes
```{r}
# Prep the data
effectsize.df <- corals.2021_wide %>%
  filter(Treatment != "Partial") 
effectsize.df$Treatment <-factor(effectsize.df$Treatment, levels = c("Uncaged","Caged"))
effectsize.df <- as.data.frame(effectsize.df) 


## Calculate the effect size for each site
# Calculating hedges g effect size (hedges.correction=TRUE)
tmp <- with(effectsize.df,
            by(effectsize.df, Site,
               function(x) cohen.d(x$All.Corals, x$Treatment, hedges.correction = TRUE)))


# Save the data for each site
hedges.pb.lagoon <- tmp$`Il Poule Lagoon`
hedges.pb.seaward  <- tmp$`Il Poule Seaward`
hedges.salo.seaward <- tmp$`Il Anglaise Seaward`
hedges.salo.lagoon <- tmp$`Il Anglaise Lagoon`
hedges.nelson <- tmp$Nelson
hedges.midbro <- tmp$`Middle Brother`
hedges.rats <-tmp$`Il de rats`
hedges.lubine <-tmp$`Il lubine`



# Combine all together for plotting
Site <- c("Il Poule Lagoon", "Il Poule Seaward", "Il Anglaise Seaward", "Il Anglaise Lagoon", "Nelson", "Middle Brother", "Il de rats", "Il lubine")

estimate <- c(hedges.pb.lagoon$estimate, hedges.pb.seaward$estimate, hedges.salo.seaward$estimate, 
              hedges.salo.lagoon$estimate, hedges.nelson$estimate, hedges.midbro$estimate, hedges.rats$estimate, hedges.lubine$estimate)

sd <- c(hedges.pb.lagoon$sd, hedges.pb.seaward$sd, hedges.salo.seaward$sd, 
              hedges.salo.lagoon$sd, hedges.nelson$sd, hedges.midbro$sd, hedges.rats$sd, hedges.lubine$sd)

hedges.df <- as.data.frame(cbind(Site, estimate, sd))
hedges.df$estimate <- as.numeric(hedges.df$estimate)
hedges.df$sd <- as.numeric(hedges.df$sd)



# Prep the data so it has the same colors as the bruvs data
hedges.plot <- hedges.df %>%
  mutate(Atoll = ifelse(Site == "Il Poule Lagoon", "Peros Banhos", 
                        ifelse(Site == "Il Poule Seaward", "Peros Banhos",
                        ifelse(Site == "Il Anglaise Seaward", "Salomon",
                               ifelse(Site == "Il Anglaise Lagoon", "Salomon",
                                      ifelse(Site == "Nelson", "Nelson",
                                             ifelse(Site== "Middle Brother", "Brothers",
                                                    "Egmont")))))))


hedges.plot$Atoll <- factor(hedges.plot$Atoll, levels=c("Brothers", "Nelson", "Peros Banhos", 
"Salomon", "Egmont"))




# Calculate grand mean
mean <- hedges.plot %>%
  summarize(mean=mean(estimate),
            sd=sd(estimate))

# add back to data
hedges.plot <- hedges.plot %>%
  add_row(Site="Overall", estimate= 0.1400624, 
          sd=0.5526944, Atoll=NA)

hedges.plot$Site <- factor(hedges.plot$Site, 
                           levels=c("Middle Brother", "Nelson", "Il Poule Lagoon", 
"Il Poule Seaward", 
"Il Anglaise Lagoon", "Il Anglaise Seaward", "Il de rats", "Il lubine", "Overall"))




# Effect size by site
p_tiles.effectsize <- ggplot(hedges.plot, aes(x=Site, y=estimate, col=Atoll)) +
   geom_point(size=c(6,6,6,6,6,6,6,6,9), 
              shape=(values=c(19,19,19,19,19,19,19,19,18)))+
  geom_errorbar(aes(ymin = estimate-sd, 
                    ymax = estimate+sd), 
                width=0.2) +
  labs (x= "", y= "Coral Effect Size") +
  theme_pubr() +
  geom_hline(yintercept= 0, linetype=2) +
    theme_pubr(base_size = 16) + 
  theme(axis.text.x = element_blank())+
  scale_color_manual(values= c("#440154FF","#3B528BFF","#21908CFF","#5DC863FF","#FDE725FF")) +
  guides(col = "none",shape="none")+
  geom_vline(xintercept=8.5, linetype="dashed")

p_tiles.effectsize

ggsave(p_tiles.effectsize,
       file="../figures/coral-effect-size.png",
       height=5, width=7)
save(p_tiles.effectsize, file="../data/coral-effect-size.RData")

```



