---
title: "bruvs-tiles"
author: "Jamie McDevitt-Irwin"
date: "3/21/2022"
output: html_document
---

Dependencies: bruvs-data-cleaning.Rmd

**Which BRUV drops should we filter out?**
These are the drops that aren't close to our tile sites. 
- Eagle
- NE PB: North of Petite Ile Coquillage, South of Ile Yeye	


**Data Frames**
bruvs.wide
bruvs.long


```{r}
library(dplyr);library(ggplot2);library(ggpubr);library(tidyr);library(car);library(lme4);library(glmmTMB);library(emmeans)
```


# Filter sites
```{r}
# Filter out drops at only near the tiles sites 
dim(bruvs.wide) # 95 X 13
bruvs.wide_tiles <- bruvs.wide %>% 
  # get rid of PB sites away from our tiles
  filter(!Island %in% c("North of Petite Ile Coquillage", "South of Ile Yeye")) %>%
  # get rid of Eagle
  filter(Region != "Eagle Island") %>%
  # new column with all the sharks added up
  mutate(All.Sharks = amblyrhynchos + ferrugineus + melanopterus + obesus)
dim(bruvs.wide_tiles) # 70 14

# How many drops per atoll
bruvs.wide_tiles %>%
  group_by(Region) %>%
  count()


# MAke a long DF
bruvs.long_tiles <- bruvs.long %>%
    filter(!Island %in% c("North of Petite Ile Coquillage", "South of Ile Yeye")) %>%
  # get rid of PB sites away from our tiles
  filter(Region != "Eagle Island")
# get rid of eagle
dim(bruvs.long_tiles) # 280  11
dim(bruvs.long) # 380  11

unique(bruvs.wide_tiles$OpCode) # 70 independent drops!

```



```{r}
lengths_data

# Filter out drops at only near the tiles sites 
dim(lengths_data) # 305 28
lengths_data_tiles <- lengths_data %>% 
  # get rid of PB sites away from our tiles
  filter(!Island %in% c("North of Petite Ile Coquillage", "South of Ile Yeye")) %>%
  # get rid of Eagle
  filter(Region != "Eagle Island")
dim(lengths_data_tiles) # 245 28

```



# Plots
```{r}
# Region X Species
names <- as_labeller(c(`amblyrhynchos` = "C. amblyrhynchos", `ferrugineus` = "N. ferrugineus",`melanopterus` = "C. melanopterus", `obesus` = "T. obesus")) 

p_sharks_species_region <- bruvs.long_tiles %>% 
  dplyr::group_by(Region,Species) %>%
  dplyr::summarize(mean_maxN = mean(MaxN)) %>%
  group_by(Region) %>%
  ggplot(aes(reorder(Region, mean_maxN), mean_maxN, fill= Species)) +
  geom_bar(stat= 'identity', position="fill") + 
  theme_pubr() +  labs(x= "", y="Relative Abundance")+
  scale_x_discrete(guide = guide_axis(angle = 60))+ 
  scale_fill_discrete(name = "Species", labels = c("C. amblyrhynchos", "N. ferrugineus", "C. melanopterus", "T. obesus"))
p_sharks_species_region 

ggsave("../figures/sharkabundance-region-species.png", 
       plot=p_sharks_species_region, width= 7, height=5)


library(viridis)
# Sharks by Region
bruvs.wide_tiles$Region <- factor(bruvs.wide_tiles$Region, levels = c("Brothers", "Nelson's Island", "PerosBanhos", "Salomon", "Egmont" ))

p_sharksXregion_tiles <- bruvs.wide_tiles %>%
  group_by(Region) %>%
  summarize(mean_maxN = mean(All.Sharks),
            sd_maxN = sd(All.Sharks),
            se_maxN = sd_maxN/ sqrt(length(All.Sharks))) %>%
  ggplot(aes(reorder(Region, mean_maxN), mean_maxN, color= Region)) + 
  geom_point(size=6) + 
  geom_errorbar(aes(ymin = mean_maxN - sd_maxN, 
                    ymax = mean_maxN + sd_maxN), 
                width=0.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x = element_blank()) +
  labs(x= "", y="Sharks (mean maxN)")+
  scale_color_viridis_d()
p_sharksXregion_tiles

ggsave("../figures/sharkabundance-region-tiles.png", 
       plot=p_sharksXregion_tiles,
       width=10, height=7)

save(p_sharksXregion_tiles, file = "../data/sharkabundance-region-tiles.RData")





# Region X Species
names <- as_labeller(c(`amblyrhynchos` = "C. amblyrhynchos", `ferrugineus` = "N. ferrugineus",`melanopterus` = "C. melanopterus", `obesus` = "T. obesus")) 

p_sharks_species_region_tiles <- bruvs.long_tiles %>% 
  group_by(Region,Species) %>%
  summarize(mean_maxN = mean(MaxN)) %>%
  group_by(Region) %>%
  ggplot(aes(reorder(Region, mean_maxN), mean_maxN, fill= Species)) +
  geom_bar(stat= 'identity') + 
  theme_pubr() +
  ggtitle("\n\nSum of mean maxN across species") + 
  labs(x= "Region", y="Sum of mean maxN (+/- SE)")+ 
  scale_fill_discrete(name = "Species", labels = c("C. amblyrhynchos", "N. ferrugineus", "C. melanopterus", "T. obesus"))

p_sharks_species_region_tiles

ggsave("../figures/sharkabundance-region-species.pdf", 
       plot=p_sharks_species_region, width= 7, height=5)


# Region X Species
bruvs.long_tiles$Region <- factor(bruvs.long_tiles$Region, levels = c("Brothers", "Nelson's Island", "PerosBanhos", "Salomon", "Egmont" ))


p_sharksXregion_tiles_species <- bruvs.long_tiles %>%
  group_by(Region, Species) %>%
  summarize(mean_maxN = mean(MaxN),
            sd_maxN = sd(MaxN),
            se_maxN = sd_maxN/ sqrt(length(MaxN))) %>%
  ggplot(aes(reorder(Region, mean_maxN), mean_maxN, color= Region)) + 
  facet_wrap(~ Species) +
  geom_point(size=6) + 
  geom_errorbar(aes(ymin = mean_maxN - sd_maxN, 
                    ymax = mean_maxN + sd_maxN), 
                width=0.2) +
  theme_pubr(base_size=16) + 
  theme(axis.text.x = element_blank()) +
  labs(x= "Region", y="Sharks (mean maxN)")+
  scale_color_viridis_d()
p_sharksXregion_tiles_species 

ggsave(p_sharksXregion_tiles_species ,
       file="../figures/sharks-region-species-maxn-tiles.png",
       width=10)
```

Plots of lengths

- no data for length of blacktip sharks from brothers? 
- but there are two blacktip sharks recorded in the bruvs (likely they couldn't be measured?)

Revisions: adding genus to species facet
```{r}

# Sharks by Region
lengths_data_tiles$Region <- factor(lengths_data_tiles$Region, levels = c("Brothers", "Nelson's Island", "PerosBanhos", "Salomon", "Egmont" ))

# New facet label names for dose variable
new.labs <- c("C. amblyrhynchos", "N. ferrugineus", "C. melanopterus", "T. obesus")
names(new.labs) <- c("amblyrhynchos", "ferrugineus", "melanopterus","obesus")


p_shark_lengths <- lengths_data_tiles %>%
  ggplot(aes(x=Region, y=Length..mm.)) + 
  facet_wrap(~ Species, scales="free_y",
             labeller = labeller(Species= new.labs))+
  geom_boxplot()+
  theme_pubr(base_size=14)+
  labs(y= "Length (mm)", x="")+
  scale_x_discrete(guide = guide_axis(angle = 60))
p_shark_lengths

ggsave(p_shark_lengths,
       file="../figures/sharks-lengths.png",
       width=10, height=8)

# removing outliers
lengths_data_tiles %>%
  filter(Species == "amblyrhynchos") %>%
  ggplot(aes(x=Region, y=Length..mm.)) + 
  geom_boxplot()+
  ylim(0,1500)+
  theme_pubr()

lengths_data_tiles %>%
  filter(Species == "amblyrhynchos") %>%
  summarize(mean= mean(Length..mm.),
            sd=sd(Length..mm.))
# 942.5383

```

# Model
Shows there is a significant difference in shark abundance across the atolls
```{r}
str(bruvs.wide_tiles)

bruvs.wide_tiles$Island <- as.factor(bruvs.wide_tiles$Island)

hist(bruvs.wide_tiles$All.Sharks) # doesn't seem zero inflated, so use normal poisson and nbinom for count data

# Try out poisson and nbinom for count data 
m1 <- glmmTMB(All.Sharks ~ Region + (1|Island), data=bruvs.wide_tiles, family = poisson)

m2 <- glmmTMB(All.Sharks ~ Region + (1|Island), data=bruvs.wide_tiles, family = nbinom2())
AIC(m1)
AIC(m2) #this one is better

summary(m2)
performance::r2(m2)  
#Warning: mu of 4.5 is too close to zero, estimate of random effect
#  variances may be unreliable.# R2 for Mixed Models

# Now try the model without the random effect
m3 <- glmmTMB(All.Sharks ~ Region, data=bruvs.wide_tiles, family = nbinom2())
summary(m3)

performance::r2(m3)  
# Conditional R2: NA
#      Marginal R2: 0.120

# Model Fit
library(DHARMa)
simres <- simulateResiduals(m3)
plot(simres) # looks good!

car::Anova(m3, type=2) # significant

# Posthoc contrasts
pairs(emmeans(m3, ~ Region))
# egmont is significantly higher than brothers, nelsons and peros
```



# Mean of sum MaxN
This will be the explanatory variable in all of our models! 
```{r}
mean.shark.abundance.tiles <- bruvs.wide_tiles %>%
  group_by(Region) %>%
  summarize(mean_maxN = mean(All.Sharks)) %>%
  ungroup()
mean.shark.abundance.tiles 
save(mean.shark.abundance.tiles, file="../data/created/mean.sum.shark.abundance.tiles.RData")
```

Looks good! 6April2023