---
title: "bruvs-data-cleaning"
author: "Jamie McDevitt-Irwin"
date: "2023-01-12"
output: html_document
---

**Data Description**
MaxN: estimate of abundance, maximum number of individuals of any given species observed at any one time on a video. Avoids double counting individuals and gives a conservative estimate of relative abundance of species. This is *count* data. 

So we have a MaxN for each species, for each 'Rig' at each drop (different drops around the island/region).


# Packages
```{r}
# load libraries
library(plyr);library(dplyr);library(ggplot2);library(ggpubr);library(tidyr);library(car);library(MASS);library(pscl);library(lmtest);library(multcomp);library(sjPlot);library(lsmeans);library(rcompanion);library(ggsignif);library(stringr);library(reshape2)

```


# Load Data
```{r}
# shark max N Data
maxN_data <- read.csv(file='../data/raw/maxN_Chagos_201903.csv', header=TRUE, sep=",")

# shark species summary data: has all the drops 
spsum_data <- read.csv(file='../data/raw/species_summary_Chagos_201903.csv', header=TRUE, sep=",")

# shark length data (updated)
lengths_data <- read.csv(file='../data/raw/BIOT_7097_UpdatedSharkLengthMeasurements_Dec2019.csv', header=TRUE, sep=",")
```


# Data Wrangling
```{r, include=FALSE}
# Summary Statistics: by island (across species)
maxN_data %>% 
  group_by(Region) %>%
  summarize(n_Drop= length(unique(Drop))) # sample size per island 
# this isn't correct, we need to include the drops that had no sharks seen

# Missing six drops that showed no sharks 
length(unique(maxN_data$Drop)) # 89
length(spsum_data$Drop) # 95
# merge these two datasets to get the drops with zero sharks

# fix the "OpCode" for drop 49 in the MaxN csv
maxN_data$OpCode <- dplyr::recode(maxN_data$OpCode, "BIOT_7097_SALO_0419_MAP_RIG3" = "BIOT_7097_SALO_049_MAP_RIG3")

# Combine the two dataframes
maxN_complete <- full_join(maxN_data, spsum_data, 
                   by = c("Drop", "Region", "Island", "Lat", 
                          "Long", "OpCode",
                          "Time.to.bait.loss..min." = "Time.to.bait.loss"))

# Make the MaxN=NA to zero
maxN_complete$MaxN <- maxN_complete$MaxN %>% replace_na(0)
sum(maxN_complete$MaxN) #405
sum(maxN_data$MaxN) #405 
# Now the six opcodes are there, but there isn't a zero value for each shark species



# Create a wide DF
# Get NAn values for every species that was not recorded at a drop, this creates a wide site by species matrix
bruvs.wide.df1 <- maxN_complete %>%
  pivot_wider(id_col= OpCode, names_from= Species, values_from= MaxN) %>%
  dplyr::select(-"NA") %>% # get rid of the NA column created from the zero six op codes
  dplyr::select(-"albimarginatus") # get rid of silvertip

bruvs.wide.df1 <- as.data.frame(bruvs.wide.df1)
bruvs.wide.df1[is.na(bruvs.wide.df1)] <- 0 # convert these NAn to zero
dim(bruvs.wide.df1) # 95 X 5


# Add back in the metadata 
meta <- spsum_data %>%
  dplyr::select(OpCode, Region, Island, Time.to.bait.loss,
                Final.drop.time..min., Depth_m, Time.in, Time.out, Species.List..MaxN.)

bruvs.wide <- meta %>%
  full_join(bruvs.wide.df1, by="OpCode")
dim(bruvs.wide) #  95 13




# Create a long DF
bruvs.long <- bruvs.wide %>%
  pivot_longer(cols= amblyrhynchos:obesus,
               names_to="Species", values_to = "MaxN")


# Create a Dataframe with all the species added up
bruvs.summary <-bruvs.wide %>%
  mutate(All.Sharks = amblyrhynchos + ferrugineus + melanopterus + obesus)

unique(bruvs.summary$OpCode) # 95 independent drops!
```

Final DFs: bruvs.wide, bruvs.long


## Raw Summaries
```{r, include=FALSE}
# Overall mean shark abundance
bruvs.summary %>% 
  summarize(mean_maxN = mean(All.Sharks)) # 4.24210 mean sharks per hour 
  
# Range of what is seen in the drops
range(bruvs.long$MaxN) # 0-12
range(bruvs.long$Depth_m) # 4.5 12.0
mean(bruvs.wide$Depth_m)
```

